\chapter*{Acknowledgements} %* means unnumbered heading
%\thispagestyle{empty} %no page numbers

The past four years have brought with them challenging and exciting times. I am immensely proud of what I have
achieved since arriving in Bristol in 2010, and of the work I have carried out during my PhD. There are,
however, many people who have helped me along the way. Here is my attempt at expressing my thanks to them:

First and foremost, the advice and support of my supervisor, Prof. Joel Goldstein, has been invaluable. Thank
you for the guidance you've provided, for providing feedback on my several thesis chapter drafts, and
generally for being available whenever I needed to speak to you! Modern day particle physics is a
collaborative field, and I also owe many thanks to my fellow analysts for their help and guidance.
Prof. Greg Heath, Emyr Clement, Luke Kreczko, Sergey Senkin and Phil Symonds have been a great team to
work with, and I pay them a compliment by saying that I would gladly work with any of them again in the
future. Special acknowledgement goes to Luke, who I have pestered from day one (and probably will continue to
do so \textemdash~ apologies in advance); your help with everything was much appreciated.

The office merry-go-round means I have shared an office with a great deal of people during
my PhD. In addition to my collaborators, to Lana, Jack, Nik, Andrew, Matt, Sam, Chris, Daniel, Christian, Tom and
all the many good friends I consider myself priveleged to have met during my time in Bristol and Geneva\ldots
thanks for the water/food/shopping/lunch/random-youtube-video/library/gym/running-breaks. And the odd deep
and meaningful conversation. We all know doing a PhD is a rollercoaster ride, and it is a pleasure to have
shared your company through the highs and the lows. The Goldney/Hillside Woodside SCR team deserve a mention
in this section\ldots being an SR has played a big part in my life in Bristol and I have enjoyed every minute
of it. Well, maybe not the 4am fire alarms and spending hours with sick students at the BRI A\&E. Neverthless,
the teams I've worked with, and indeed most of the students, have been excellent and I am so glad I decided to apply
to be an SR because I have made many lifelong friends as a result.

It would be remiss of me to complete this round of thanks without mentioning those who have accompanied me in
my sporting endeavours, especially my teammates in the University of Bristol Athletics and Cross Country club.
Despite all being so busy with myriad activities in life, I always knew that on the track I could find a
welcome break from academia and sporting camaraderie. On that note, how could I forget Bristol's famous
victory in the 2015 Bubble Chamber Cup. Robin, Mark, Daniel, Sudan, David and Ed\ldots WE DID IT!!! Ryan, back
over to you to take charge next year, expectations are high.

And to finish, I would like to express my gratitude to my family for their steadfast and unwavering support
and encouragement that has brought me to this point. I know it's a clich\'{e}, but this definitely would not
have been possible without you. Thank you.
